A Quantitative Genetic Linked Selection Model fit to the Negative Selection Process in Humans

### 2023-07-03 manuscript/manuscript.tex
minor ms changes

>>>>

\begin{figure}[htbp] \centering
    \includegraphics[width=\textwidth]{figures/figure_6.pdf}

    \caption{Evidence that negative selection signal remains. (A) Residuals
        from the YRI CADD 6\% model plotted against the average LoF selection
        coefficient across genes in a megabase window (estimated from
        \cite{Agarwal2023-un}). Our model is systematically over predicting
        diversity in regions estimated to be sensitive to LoF variants. The
        ordinary least squares (OLS) estimate suggests that 2.1\% of the
        variance in residuals can be explained by reductions caused by the
        local sensitivity to LoF mutations. (B) Residuals from the YRI CADD 6\%
        model plotted against the fraction of CADD 6\% basepairs in the
        megabase window. Here, only 0.8\% of the variance is explained by
        remaining spatial variance in CADD 6\% regions (blue). Overlaid is the CADD
        2\% OLS curve (orange). }

  \label{fig:figure-6}
\end{figure}
